%-------------------------
	% Resume in Latex
	% Author : Gabriel Sison
	% Based off of: https://github.com/sb2nov/resume
	% License : MIT
	%------------------------
	
	
	\documentclass[letterpaper,11pt]{article}
	\usepackage{latexsym}
	\usepackage[empty]{fullpage}
	\usepackage{titlesec}
	\usepackage{marvosym}
	\usepackage[usenames,dvipsnames]{color}
	\usepackage{verbatim}
	\usepackage{enumitem}
	\usepackage[hidelinks]{hyperref}
	\usepackage{fancyhdr}
	\usepackage[english]{babel}
	\usepackage{tabularx}
	\usepackage{fontawesome5}
	\usepackage{multicol}
	\setlength{\multicolsep}{-3.0pt}
	\setlength{\columnsep}{-1pt}
	\input{glyphtounicode}
	\pagestyle{fancy}
	\fancyhf{} 
	\fancyfoot{}
	\renewcommand{\headrulewidth}{0pt}
	\renewcommand{\footrulewidth}{0pt}
	% Adjust margins
	\addtolength{\oddsidemargin}{-0.6in}
	\addtolength{\evensidemargin}{-0.5in}
	\addtolength{\textwidth}{1.19in}
	\addtolength{\topmargin}{-.7in}
	\addtolength{\textheight}{1.4in}
	\urlstyle{same}
	\raggedbottom
	\raggedright
	\setlength{\tabcolsep}{0in}
	% Sections formatting
	\titleformat{\section}{
	  \vspace{-7pt}\scshape\raggedright\Large\bfseries
	}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]
	\pdfgentounicode=1
	
	
	\newcommand{\resumeItem}[1]{
	  \item\normalsize{
		{#1 \vspace{-3pt}}
	  }
	}
	\newcommand{\resumeSubheading}[4]{
	  \vspace{-3pt}\item
		\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
		  \textbf{#1} & \textbf{\small #2} \\
		  \textit{\small#3} & \textit{\normalsize #4} \\
		\end{tabular*}\vspace{-7pt}
	}
	\newcommand{\resumeSubheadingContinue}[2]{
	  \vspace{-3pt}
		\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
		  \textit{\small#1} & \textit{\small #2} \\
		\end{tabular*}\vspace{-7pt}
	}
	\newcommand{\resumeProjectHeading}[2]{
	  \vspace{-3pt}\item
		\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
		  \textbf{#1} & \textbf{\small #2} \\
		\end{tabular*}\vspace{-7pt}
	}
	\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{0pt}}
	\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
	\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
	\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
	\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}
	
	\begin{document}
    \begin{center}
        % NAME
        {\Huge\scshape Anthony Gorman} \\
	\large Chicago, IL\\
	\footnotesize
	\href{mailto:awgorman@liberty.edu}
	{\raisebox{-0.2\height}\faEnvelope\  \underline{awgorman@liberty.edu
	}} ~ 
        \href{github.com/AnthonyGorman}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/AnthonyGorman}}
	\end{center}

	\section{Education}
	\resumeSubHeadingListStart

	% MAIN INFORMATION
	\resumeSubheading
	{Liberty University}{Lynchburg, VA}
		{Bachelor of Science in Computer Science and Mathematics}{Fall 2021 - Spring 2025}
		\resumeSubHeadingListEnd


	\section{Experience}
		\resumeSubHeadingListStart
		
			% COMPANY 1
			\resumeSubheading
		{Argonne National Laboratory}{Lemont, IL}{Computer Vision Intern}
		{January 2023 - April 2023}
		\resumeItemListStart
			\resumeItem{Integrated 7 state-of-the-art object detection algorithms into Python modules to inference on vehicles in various weather conditions.}
			\resumeItem{Automated model evaluation with Bash scipts that deploy virtual environments and iterate through data directories.}
			\resumeItem{Presented formal research to a panel of scientistiguing presentation.}
		\resumeItemListEnd

		
			\resumeSubheading
		{Huntington Learning Center}{Mokena, IL}{Mathematics Teacher}
		{May 2022 - August 2022}
		\resumeItemListStart
			\resumeItem{Significantly improved SAT and ACT scores of over 10 students through rigorous education.}
			\resumeItem{Challenged students to think critically through personalized icebreaker exercises.}
			\resumeItem{Quickly got promoted to train incoming graduates to tutor students in both reading and math.}
		\resumeItemListEnd

		
	\resumeSubheading
	{Liberty School of Engineering}{Lynchburg, VA}{Assistant Researcher}
	{March 2022 - December 2022}
	\resumeItemListStart
	\resumeItem{Conducted literature review of surrogate models and summarized content for a doctoral mentor.}
	\resumeItem{Researched machine learning algorithms for discovering inter-atomic potentials.}
	\resumeItem{Organized a 7-person research team for a school club to foster academic growth.}
	\resumeItemListEnd

		
	\resumeSubheading
	{AI competition Club}{Lynchburg, VA}{President}
	{Fall 2022 - Current}
	\resumeItemListStart
	\resumeItem{Adopted a dying club with no returning members and quadrupled expected attendance (5 members to 20 active members).}
	\resumeItem{Advertised club to all lower-level computer science classes.}
	\resumeItem{Rebranded from Kaggle Club to Artificial Intelligence Competition Club.}
	\resumeItemListEnd

	\resumeSubHeadingListEnd
	
	\section{Personal Projects} 
    \resumeSubHeadingListStart

        % Project 1
        \resumeProjectHeading
		{Resume Builder-\href{github.com/AnthonyGorman/ResumeBuilder}{\raisebox{-0.2\height}\ \underline
		{github.com/AnthonyGorman/ResumeBuilder}}}{Winter 2023}
		\resumeItemListStart
		\resumeItem{Using a Go backend, Resume Builder collects input fre user and creates a LaTex resume.}
		\resumeItemListEnd

		% Project 2
		\resumeProjectHeading
		{YOLO Demo-\href{github.com/AnthonyGorman/YOLODemo}{\raisebox{-0.2\height}\ \underline
		{github.com/AnthonyGorman/YOLODemo}}}{Spring 2023}
		\resumeItemListStart
		\resumeItem{The YOLO Demo was a project done to learn the markdown language and to teach object detection to the AI Competition Club.}
		\resumeItemListEnd
	\resumeSubHeadingListEnd
	\section{Technical Skills}

    \vspace{-7pt}
    \begin{itemize}
    [leftmargin=0.15in, label={}]\small{\item{
        % LANGUAGES
        \textbf{Languages}{: Go; Python; C++; Java; SQL; x86 Assembly (Linux)} \\
		\textbf{Developer Tools}{: Visual Studio (Code); Anaconda; Cypress; Codeium; Git}
	}}
	\end{itemize}
	\end{document}